---
title: "Phoebe_Frankie_whales"
author: "Phoebe Hird"
date: "2024-05-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
R markdown for whale Plot deconstruction. The plot came from a published paper in Population Ecology journal. https://esj-journals.onlinelibrary.wiley.com/doi/full/10.1002/1438-390X.1014

Plot caption: Whale sighting data comparison between Norm's Seat and Frenchman's lookout in 2010 over 120 hours of observation.

Issues with the original plot:
1. colour scheme is poor
2. used a bar plot for continous (time) data 
3. other presentation issues (grid lines)

The plan is to recreate the plot with geom smooth lines, correct the colour scheme. 

We used a Plot digitiser online tool to extract data from the image. 

We then imported the extracted data as a .csv file to rebuild the plot.

```{r}
library(tidyverse)
```


## Start plot deco
```{r}
whale_data
```

```{r}
ggplot(data = whale_data_edit, mapping = aes(x = Date, y = no..whales.passing)) + 
  geom_point(mapping = aes(color = Location)) + 
  geom_smooth(aes(x=as.numeric(factor(Date)), color=Location), se =FALSE) +
  theme_classic()+
  theme(axis.text.x = element_text(angle=90, hjust=1))+labs(
    x = "Date",
    y = "No. whales passing",)+
  scale_fill_brewer(palette="Identity")

```

```{r}
ggsave("Plot_deco_PF.pdf")

```
# Assignment 2 work
Exported turtle data from QFISH and tidied it in Excel before uploading into R using the readr package to load in the .csv file. 

```{r}
library(readr)
data <- read_csv("TurtlesFINAL.csv")
library(tidyverse)
```
```{r}
ggplot(data = TurtlesFINAL, mapping = aes(x = Year, y = Turtles)) + 
  geom_point(mapping = aes(color = Location)) +
  geom_smooth(aes(=Location)) +
scale_color_manual(values=c("magenta","orange","blue"))+
  theme_classic()+
  labs(
    x = "Year",
    y = "Turtles (count)",)+
  labs(title = "Fuel efficiency generally decreases with engine size")

```

